Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-09-12 paper/proof/13636_2018_138_MOESM1.tex
proofread last equation of appendix

The discriminant of the above equation is
\[
D=\dfrac{4\sigma^2}{Nr}
\left(
\dfrac{\sigma^2}{Nr\xi^2}
+
2(1-r)
\right),
\]
which is a positive number because $r<1$.
The bandwidth $B$ of $\boldsymbol{\hat{\psi}}$ is given by the difference between the two solutions of the quadratic equation, that is:
\[
B = 
\sqrt{D} =
\dfrac{2\sigma}{\sqrt{N r}}
\sqrt{\dfrac{\sigma^2}{N r \xi^2} + 2 (1-r)}
.
\]
Now, let us express the parameter $\sigma$ as a function of some
required bandwidth $B$ at some cutoff threshold $r$. After having
raised the above to its square and rearranged the terms, we obtain
another quadratic equation, yet of the variable $\mbox{\ensuremath{\sigma}}^{2}$:
\[
\dfrac{4}{N^2 r^2 \xi^2} (\sigma^2)^2 + \dfrac{8 (1-r)}{N r} \sigma^2 - B^2 = 0.
\]
We multiply the equation by $\tfrac{1}{8} N^2 r^2 \xi^2 \neq 0$, thus yielding
\[
\dfrac{1}{2} (\sigma^2)^2
+
N r (1-r) \xi^2 \sigma^2
-
\dfrac{N^2 r^2 \xi^2 B^2}{8}
= 0.
\]
The discriminant of the above equation is equal to:
\[
D^\prime = N^2 r^2 \xi^2 \left(\xi^2 (1-r)^2 + \tfrac{1}{4}B^2\right).
\]
Because this discriminant is strictly positive, the equation has two roots.
Yet, only the smallest of the two satisfies $\sigma^2 < \xi^2$.
Therefore, we have
\[
\sigma^{2}=
N r (1-r)
\left(
\sqrt{1 + \left(\dfrac{B}{2\xi (1-r)}\right)^2}
- 1\right) \xi^2 
.
\]
If the filter bank has to be approximately orthogonal, we typically
set $B$ to $B=\left(1-2^{-1/Q}\right)\times\xi$.
We conclude with the following closed form for $\sigma$:

>>>>

The discriminant of the above equation is
\[
D=\dfrac{4\sigma^2}{Nr}
\left(
\dfrac{\sigma^2}{Nr\xi^2}
+
2(1-r)
\right),
\]
which is a positive number because $r<1$.
The bandwidth $B$ of $\boldsymbol{\hat{\psi}}$ is given by the difference between the two solutions of the quadratic equation, that is:
\[
B = 
\sqrt{D} =
\dfrac{2\sigma}{\sqrt{N r}}
\sqrt{\dfrac{\sigma^2}{N r \xi^2} + 2 (1-r)}
.
\]
Now, let us express the parameter $\sigma$ as a function of some
required bandwidth $B$ at some cutoff threshold $r$. After having
raised the above to its square and rearranged the terms, we obtain
another quadratic equation, yet of the variable $\mbox{\ensuremath{\sigma}}^{2}$:
\[
\dfrac{4}{N^2 r^2 \xi^2} (\sigma^2)^2 + \dfrac{8 (1-r)}{N r} \sigma^2 - B^2 = 0.
\]
We multiply the equation by $\tfrac{1}{8} N^2 r^2 \xi^2 \neq 0$, thus yielding
\[
\dfrac{1}{2} (\sigma^2)^2
+
N r (1-r) \xi^2 \sigma^2
-
\dfrac{N^2 r^2 \xi^2 B^2}{8}
= 0.
\]
The discriminant of the above equation is equal to:
\[
D^\prime = N^2 r^2 \xi^2 \left(\xi^2 (1-r)^2 + \tfrac{1}{4}B^2\right).
\]
Because this discriminant is strictly positive, the equation has two roots.
Yet, only the smallest of the two satisfies $\sigma^2 < \xi^2$.
Therefore, we have
\[
\sigma^{2}=
N r (1-r)
\left(
\sqrt{1 + \left(\dfrac{B}{2\xi (1-r)}\right)^2}
- 1\right) \xi^2 
.
\]
If the filter bank has to be approximately orthogonal, we typically
set $B$ to
\[
B = 
\left(\sqrt[Q]{2} - \dfrac{1}{\sqrt[Q]{2}} \right)
\times \xi.
\]
We conclude with the following normalized closed form for $\sigma$:
\[
\dfrac{\sigma}{\xi} = \sqrt{N r (1-r)}
\left(
\sqrt{
1 +
\dfrac{\left(\sqrt[Q]{2} - \dfrac{1}{\sqrt[Q]{2}} \right)^2}{
4 (1-r)^2
}}
- 1\right).
\]
